The mzsql project

### 2025-03-20 README.qmd
Updating README with new examples

Ensure `RaMS`, `DBI`, and `duckdb`/`RSQLite` are all installed from CRAN.

```{r make database, eval=FALSE}
library(RaMS)
msdata <- grabMSdata(list.files("demo_data", pattern = "mzML", full.names = TRUE))

@@

conn <- dbConnect(RSQLite::SQLite(), "demo_data/msdata.sqlite")
# conn <- dbConnect(duckdb::duckdb(), "demo_data/msdata.duckdb")
chr_statement <- "SELECT * FROM MS1 WHERE mz BETWEEN ? AND ?"
chrom <- dbGetQuery(conn, chr_statement, params=pmppm(118.0865, 10))
dbDisconnect(conn)
plot(chrom$rt, chrom$int, type = "l")
```

>>>>

Some simple demo code shown below for MS1 and MS2 table creation to illustrate what the converters do:

```{r make database, eval=FALSE}
# Ensure `RaMS`, `DBI`, and `duckdb`/`RSQLite` are all installed from CRAN.
library(RaMS)
msdata <- grabMSdata(list.files("demo_data", pattern = "mzML", full.names = TRUE))

@@

conn <- dbConnect(RSQLite::SQLite(), "demo_data/msdata.sqlite")
# conn <- dbConnect(duckdb::duckdb(), "demo_data/msdata.duckdb")
chr_statement <- "SELECT * FROM MS1 WHERE mz BETWEEN ? AND ? ORDER BY filename, rt"
chrom <- dbGetQuery(conn, chr_statement, params=pmppm(118.0865, 10))
dbDisconnect(conn)
plot(chrom$rt, chrom$int, type = "l")
```
